### 2020-01-06 Draft/Draft.tex
periodic linear model added

\section{Extension of LACC to non-linear case}

>>>>

\subsubsection{Linear coupled model with periodicity}
\label{sec:linvar}
It is an interesting exercise to introduce some form of internal periodic variability into the system, especially in order to access how such an intrinsic periodicity may (or may not) couple with the externally induced `periodicity' due to the windowing in the \textsf{SCDA} process. We note that such periodic variabilities in climate systems are natural, e.g. seasonal variability in the weather; this form of variability is thermally driven and we may include it in the ocean sub-component of the model\footnote{We are particularly interested in introducing a low-frequency variability which is the why this term is included in the slower ocean component instead of the atmosphere.} by adding a periodic term of the form $\vams{I}{v}\csin(\vars{\omega}{v} t)$ to \eqref{eq:linmodel1}. In figure \ref{fig:11}, we present the results for this model. Notably in the last panel 3 in figure \ref{fig:11}, we find that the ocean suffers from a loss in terms of the accuracy of the $\textsf{SCDA}$ when the periodic variability term is present. \textsf{<reason>}
\centering\includegraphics[width=78mm]{{Fig11a}.png}\vspace*{0.1in}
\centering\includegraphics[width=78mm]{{Fig11b}.png}\vspace*{0.1in}
\includegraphics[height=21.5mm]{{Fig11c}.png}
\includegraphics[height=21.5mm]{{Fig11d}.png}
\caption{{\small \tit{Top panel} 1: Cross- and auto-correlation functions for $\vams{I}{v} = \sigma_\mathsf{F}/2$ and $\omega_\mathsf{v} = 20.0$. All other parameters are valued as before.\\
\tit{Middle panel} 2: 1-member \textsf{SCDA} simulation for $\vams{I}{v} = \sigma_\mathsf{F}/2$ and $\omega_\mathsf{v} = 20.0$.\\
\tit{Bottom panel} 3: $\delta\boldsymbol{\sigma}_\mathsf{periodic} - \delta\boldsymbol{\sigma}_\mathsf{non-periodic}$ for $\vams{I}{v} = \sigma_\mathsf{F}/2$ and $\omega_\mathsf{v} = 20.0$.}}
\label{fig:11}
\section{Extension to non-linear case}
